### 2016-09-07 analysis-note-v2/analysis-2.tex
added the contamination plots instead of the pi0 production yield plots, section 4.5.2 figure 4.19

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Phi.png}
\caption{The coherent channel acceptance ratios as a function of the kinematic 
variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and 
$\phi$ (bottom right). }
\label{fig:coh_acceptance _ratios}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the 
kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
left), and $\phi$ (bottom right).}
\label{fig:incoh_acceptance _ratios}
\end{figure}

>>>>

Figure \ref{fig:cont_yield} presents the measured coherent and incoherent 
$\pi^{0}$ contmaination with respect to the measured DVCS events. On both 
channels, the contamination increases strongly with -$t$, with a mean of 2$\%$ 
(6$\%$) for the coherent (incoherent) channel. \\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Phi.png}
\caption{The coherent channel acceptance ratios as a function of the kinematic 
variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and 
$\phi$ (bottom right). }
\label{fig:coh_acceptance _ratios}
\end{figure}

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the 
kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
left), and $\phi$ (bottom right).}
\label{fig:incoh_acceptance _ratios}
\end{figure}

\begin{figure}[tpb]
\includegraphics[scale=0.4]{fig_updated/T_ratio_pi0_dvcs_Coh_t.pdf}
\includegraphics[scale=0.4]{fig_updated/T_ratio_pi0_dvcs_InCoh_t.pdf}
\caption{The experimental coherent (left) and incoherent (right) $\pi^{0}$ 
contamination with respect to the experimental DVCS events as a function of the 
transfered momentum squared -$t$. The data is integrated over the kinematical 
variables $Q^2$, $x_B$, and $\phi$.  }
\label{fig:cont_yield}
\end{figure}
